---
title: "Naa10-koy"
author: "Andrew Garcia"
date: "2023-01-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Naa10 KO/Y and WT/Y NAA10 quantification
Heart and liver lysates from biological replicates (n = 8) of Naa10 KO/Y (n = 4)
and Naa10 WT/Y mice were immunoblotted. Blots of respective organ lysates were
repeated twice.


##Data
```{r}
library(tidyverse)

heart <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRL7DxP9iAmk45qq_UyZQTG7nRE5qi2VIBQ3Ln4gY2tIBLUNiNmFdT1QkoAxlOORA/pub?gid=1850069092&single=true&output=csv", header = T)


```

```{r}
head(heart)

##double-check genotypes of biological replicates
```


```{r}
##switched Name and Replicate fromn integers to factors
heart$Name <- as.factor(heart$Name)
heart$Replicate <- as.factor (heart$Replicate)
heart$Genotype <- as.factor(heart$Genotype)
heart$Organ <- as.factor(heart$Organ)

head(heart)

##changed Name and Replicate from integer data to replicate data
```
##distribution of NAA10 signal
```{r}
ggplot(heart,aes(x = Genotype,
                 y = Normalized.Signal,
                 color = Name,
                 shape = Replicate))+
  geom_point()+
  ylab("NAA10 signal normalized to
       REVERT total protein stain")+
  ggtitle("NAA10 levels in Naa10
          heterozygous mutant heart")

##if we added jitter as another layer, the data points would be duplicated
##in the resultant plot!
```




##Group-mean datasets in dplyr
```{r}
#I am more familiar with using summarySE in Rmisc to generate a dataframe that contains group means


```


#Summary data of Naa10 het heart and hypothesis testing
```{r}

install.packages("Rmisc", repos = "http://cran.us.r-project.org")

```

##Grouping by Genotype and Organ
```{r}
##Summary statistics for Normalized NAA10 signal
##Possible groupings: genotype, replicate, organ
##Replicate grouping pertains to replicate blot grouping

library(Rmisc)
heart_sum <- summarySE(heart, measurevar="Normalized.Signal", groupvars=c("Organ","Genotype"))

heart_sum
```


##Genotype group mean
```{r}
##Normalized NAA10 signal is grouped by genotype.
##N = 6 for both genotypes because the 3 biological replicates in each genotype were assayed twice
##this gives me the group mean dataframe that I will need to layer onto the plot of individual observartions

heart_sum1 <- summarySE(heart, measurevar="Normalized.Signal", groupvars=c("Genotype"))

heart_sum1
```

```{r}
install.packages("ggplot2",
                 repos ="http://cran.us.r-project.org")

```


```{r}
#group means plus standards
#essentially looking to plot this onto the individual data plot
ggplot(heart_sum1, aes(x = Genotype, y = Normalized.Signal))+
  geom_point()+
  geom_errorbar(aes(ymin = Normalized.Signal - sd,
                ymax = Normalized.Signal + sd))
```

##individual data and group means plot
```{r}
#ggplot(heart) plots Normalized.Signal as a function of Genotype
#geom_point plots individual observations on this plot
#geom_errorbar points to my group means df heart_sum1 and the bounds of the mean+/- standard error bar
#the successive geom_point plots the mean; specify color so it does not conflict with the color call in the first geom_point

library(ggplot2)
ggplot(heart,aes(x = Genotype,
                 y = Normalized.Signal))+
  geom_point(aes(color = Name,
                 shape = Organ),
             alpha = 2.0,
             size = 2,
             position = position_jitterdodge())+
    geom_boxplot(outlier.shape = NA,
               alpha = 0.1)+
  stat_summary(fun= mean, geom="point",
               shape=3, size=5,stroke = 1,color="red", fill="black")+
  geom_errorbar(data = heart_sum1,
                aes(ymin = Normalized.Signal-sd,
                    ymax = Normalized.Signal+sd,
                    width = 0.2))+
  geom_point(data = heart_sum1,
             size = 0.4,
             alpha = 1.0,
             color = "red")+
  xlab("Naa10 genotype")+
  ylab("NAA10 signal normalized to
       REVERT total protein stain")+
  theme_bw(base_size = 12, base_family = "Helvetica")
```

###Organ on X-axis
```{r}
ggplot(heart,aes(x = Organ,
                 y = Normalized.Signal,
                 fill = Genotype))+
  geom_point(aes(shape = Genotype),
             alpha = 2.0,
             size = 2,
             position = position_jitterdodge())+
  geom_boxplot(outlier.shape = NA,
               alpha = 0.1)+
  xlab("Naa10 genotype")+
  ylab("NAA10 signal normalized to
       REVERT total protein stain")+
  theme_bw(base_size = 12, base_family = "Helvetica")
```

###main fig; Organ fill?
```{r}
library(ggplot2)
ggplot(heart,aes(x = Genotype,
                 y = Normalized.Signal,
                 fill = Organ,
                 alpha = 2.0))+
  geom_point(aes(shape = Organ),
             alpha = 2.0,
             size = 2,
             position = position_jitterdodge())+
  geom_boxplot(outlier.shape = NA,
               alpha = 0.1)+
  xlab("Naa10 genotype")+
  ylab("NAA10 signal normalized to
       REVERT total protein stain")+
  theme_bw(base_size = 12, base_family = "Helvetica")
```



##Unpaired t-test of NAA10 signal grouped by Genotype

Null hypothesis: there is no mean difference in NAA10 signal
between Naa10 male genotypes

Alternative: there is a difference in NAA10 signal between Naa10
male genotypes
```{r}
t.test(heart$Normalized.Signal~heart$Genotype,
       paired = F,
       var.equal = FALSE)
```


According to Welch's two sample t-test, there is a significant difference in
NAA10 signal between Naa10 female genotypes (t = -14.5, df = 9.9, p < 0.05).


##paired t-test of NAA10 signal between replicates of individual animals

Null hypothesis: there is no difference in NAA10 signal of individual livers on replicate blots
Alternative hypothesis: there is a difference in NAA10 signal of individual livers on replicate blots

According to the paired t-test (t = -0.18, df = 5, p = 0.87),
I fail to reject the null hypothesis. Ie, when I analyze the normalized NAA10 signal
in technical replicates of each biological replicate, there is no difference in the
NAA10 signal between technical replicates.

#Other plot ideas
```{r}
#plotted error bars for intra-subject variation
#need also group error bar (mean +/- sd)
gg_heart <- ggplot(heart,aes(x = Genotype,
                 y = Normalized.Signal,
                 color = Name,
                 shape = Replicate))+
  geom_point()+
  ylab("NAA10 signal normalized to
       REVERT total protein stain")+
  ggtitle("NAA10 levels in Naa10
          heterozygous mutant heart")

gg_heart+
  geom_errorbar(aes(ymin = Avg..Norm..Signal-Std..Dev.,
                           ymax = Avg..Norm..Signal+Std..Dev.,),
                position = "dodge",
                width = 0.2)

```

```{r}
ggplot(heart,aes(x = Genotype,
                 y = Normalized.Signal,
                 color = Name,))+
  geom_point()+
  geom_errorbar(aes(ymin = Avg..Norm..Signal-Std..Dev.,
                    ymax = Avg..Norm..Signal+Std..Dev.,
                    width = 0.2))+
  ylab("NAA10 signal normalized to
       REVERT total protein stain")+
  ggtitle("NAA10 levels in Naa10
          heterozygous mutant heart")
```


###Plotted by biological replicate
```{r}
ggplot(heart, aes(x = Name,
                  y = Normalized.Signal,
                  shape = Replicate,
                  color = Genotype))+
         geom_point()+
  xlab("sample ID")+
  ylab("NAA10 signal normalized to
       REVERT total protein stain")+
   ggtitle("NAA10 levels in Naa10
          heterozygous mutant heart")

```




This plots absolute signal and indicates biological replicate (color) and
technical replicate (shape)

If I loaded a control sample (e.g., WT/Y or a pooled sample of all
biological replicates in the WB dataset),
I could plot fold-change.

However, I am limited to plotting the absolute value of NAA10 signal.
```{r}
heart_fold <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQ6Zsk-kGVqB3DlzX_VtZE5cRNqqM5NX5rfdp5t1kuEkH6PAKf76ozEFmqklqKIFZqWvjzcx_mOV5K6/pub?gid=194880494&single=true&output=csv",
                       header = T)

head(heart_fold)
```